### 2017-06-07 paper/documents/5.conclusion.tex
- update paper

Classify the player roles is not easy. We asking \textit{Dota 2} experts to manually classify the player roles. The responses were highly divergent among them. This illustrates that the classification tasks is difficult, even for human experts. Our data set from the professional tournament (

\subsection{Conclusion}
\label{sec:conclusion}

>>>>

Classify the player roles is not easy. We asking \textit{Dota 2} experts to manually classify the player roles. The responses were highly divergent among them. This illustrates that the classification tasks is difficult, even for human experts. Our data set from the professional tournament (Kiev Major 2017 and \textit{The International 2016}) with 8419 data set, We separated into 70\% for training data and 30\% the rest for testing data. We also classified our data set with the same attributes but with a reduced set of classes (\textit{carry}, \textit{support}) inspired by Gao et al. \cite{gao2013classifying}, classification with our attributes achieved a higher accuracy for our data set. A direct comparison is not possible since the data sets differ. Still, the result indicate that classification with a reduced set of classes works well and could already be employed for many applications. Summarizing, we can state that the full set of classes shows promising results but also highlights that, although these classes are accepted by \textit{Dota 2} experts, some are ambiguous even to humans manually labeling the data.

\subsection{Conclusion and Future Work}
\label{sec:conclusion}
